Seismic parameter estimation and the Canadian crust

### 2013-02-16 paper/draftBP.tex
paper

%% -----------------------------------------------%%
\section{Results}
Ideas:
Reliability of methods:
  Compare bulk properties garnered from MB to Kan Approach.
  Compare Kan approach values to others in literature
  Canada wide -> Regional

\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{thompsonComparison}
  \caption{A picture of a gull.}
\end{figure}

>>>>

%% -----------------------------------------------%%
\section{Results}
As regional studies exist which utilize similar methods and have corrisponding parameter estimates for some of the stations used in this study it is possilbe to directly compare values to those previously published. A comprehensive study in the Hudson Bay region of the Canadian Shield (Thomson et. al., 2010) uses an approach similar to the Zhu and Kanamori method provides estimates for $H$ and $R=/frac{V_P}{V_S}$ for 35 stations. 5 stations with $R$ estimates above 1.8 are removed due to the uncertainty surrounding these high values. Both datasets are plotted in Figure~\ref{fig:thompsonComp}. The Pearson correlation coefficient between these datasets is 0.49. [Compare this value to uncertainty / deviation in the data? ].

Directly comparing $V_P$ estimates processed with the MB algorithm is not possible as this method has not been employed in publication. However, comparisons can be made to active source records for experiments within close proximity to a given seismic station (Figure~ \ref{fig:activeComp}. The correlation between these datasets is 0.235. [This is low, explain here?]. Another method of determining the reliability of estimates is to check the $/frac{V_P}{V_S}$ ratio taken from the Kanamori approach to the $/frac{V_P}{V_S}$ value computed from the MB approach. These values, working with the same data, preprocessed using the same methods and tools should be equal. Selecting only those stations who have an error of less than +/-0.05 $R$, 132 stations, we get a correlation of 0.57. Reducing the error tolerance and selecting stations with less than +/-0.01 $R$, leaving 31 of the cleanest stations, we get a correlation coefficient of 0.95.

\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{thompsonComparison}
  \caption{Comparison of $\frac{V_P}{V_R}$ data processed for this study with data from Thomspson et. al. (2010).}
  \label{fig:thompsonComp}
\end{figure}

\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{activeSourceComparison}
  \caption{Comparison of $V_P$ estimates from the MB algorithm with active source $V_P$ recordings. Stations selected if active source experiment locations within 1 degree of latitude / longtitude.}
  \label{fig:activeComp}
\end{figure}
